

---
title: "Project"
author: "Your name is here"
output:
  word_document: default
  pdf_document: default
---


1. (6 points for collecting data) Load Your Data from excel file into Rstudio. 


```{r}

data=read.csv("mydata.csv", stringsAsFactors = T)


```

2.Provide summary of data.

```{r}

summary(data)

```


3.(2points) Create a bar plot for hair color of men. 

```{r}



    
```


4.(2points) Create a pie chart for hair color of women. 


```{r}


```
       

5.(2points) Construct histogram for height of men. (Number of bars can be choosen by default in R-studio) 




```{r}




```





6.(2points) Construct histogram for shoe size for women. (Number of bars can be choosen by default in R-studio)
```{r}



```






7.(2points)	Construct two Box Plots (one for height of men and another for height of women) on the same plot.

```{r}



```



8.(1points) Compare these two box plots and describe the differences between these two box plots. Does any boxplot have outliers? If so, how many outliers? 



9.(2points) Construct two Box Plots (one for size of shoes for men and another for size of shoes for women) on the same plot.


```{r}



```




10.(1points) Compare these two box plots and describe the differences between these two box plots. Does any boxplot have outliers? If so, how many outliers? 




11.(2points) Construct a 90% confidence interval for the estimate of mean of men's height. 

```{r}



```

**Write a statement that correctly interprets the confidence interval.**




12.(2points) Construct a 95% confidence interval for the estimate of mean of women's height. 

```{r}




```

**Write a statement that correctly interprets the confidence interval.**



13.(2points) Construct a 94% confidence interval for the estimate of mean of shoe size for women. 

```{r}



```

**Write a statement that correctly interprets the confidence interval.**







14. (4 points) Write two claims for any two different variables of your data (Height_M or Height_W or Size_Shoes_M or Size_Shoes_W). Make your claim as alternative hypothesis and show that a Null hypothesis is wrong, so it means that an  alternative hypothesis (a claim) is   true. Each claim should have different comparison sign: less, greater or not equal.

Please indicate:
1)	What is your claim? 
2)	What is the opposite statement?
3)	What is null and alternative hypothesis. 
4)	What is p-value.
5)	Write conclusion about your claim. 


Example: 

1) Claim: The average (mean) size of shoes for women is less than 9. 

2) Opposite statement: The average size of shoes for women is greater or equal 9. 

3) H_0: mean=9
   H_1: mean<9
   
 4) Creat R-code to find p-value

t.test(data$Size_Shoes_W, mu=9, alternative="less")

5) Write Conclusion: Since  p-value = 0.001507<alpha=0.05, we reject H_0. We have enough evidence to support the claim.

Part a)

**1) Claim: **

**2) Opposite statement:**

**3) H_0: mean   ;H_1: mean   **

   
**4) Creat R-code to find p-value**

```{r}




```

**5)	Write conclusion about your claim. **


Part b)

**1) Claim: **

**2) Opposite statement:**

**3) H_0: mean    ; H_1: mean   **
   
**4) Creat R-code to find p-value**

```{r}



```

**5)	Write conclusion about your claim. **


15.(2points) Compare mean of height of men and mean of height of women. You can make a claim with any sign that you think is true (less, greater or not equal). 

Please indicate:

1)	What is your claim? 

2)	What is your opposite statement?

3)	What is null and alternative hypothesis. 

4)	What is p-value.

5)	Write your conclusion about your claim. 


Example: 

1) Claim: The mean height of men is greater than the mean height of women.

2) Opposite statement: The mean height of men is less or equal to the mean height of women.

3) H_0: mean of height of men=mean of height of women. 

   H_1: mean of height of men>mean of height of women. 

4) You type R-code to find p-value

t.test(data$Height_M, data$Height_W, alternative="greater")

5) Write conclusion: Since p-value =  1.571e-14 < alpha=0.05, we reject H_0. We have enough evidence to support the claim.

**1) Claim: **

**2) Opposite statement:**

**3) H_0: mean      ;  H_1: mean   **
   
**4) Creat R-code to find p-value**


```{r}


```
**5)	Write conclusion about your claim. **



16.(2points) Compare mean of shoe size of men and mean of shoe size of women. You can make a claim with any sign that you think is true (less, greater or not equal). 

**1) Claim: **

**2) Opposite statement:**

**3) H_0: mean      ;  H_1: mean   **
   
**4) Creat R-code to find p-value**

```{r}



```

**5)	Write conclusion about your claim. **


17) (2points) Construct a scatter plot for height of men (x-axis) and size of men's shoes (y-axis)



```{r}



```

18) (2points) Find a linear correlation coefficient between height of men and size of men's shoes .


```{r}



```
  
  
**What is a linear correlation coefficient?**


19) (2points) Find regression line for height of men (x-variable) and size of men's shoes (y-variable)


```{r}



```

**What is a regression line?**
 
20) (2points) Construct a scatter plot for height of men (x-axis) and size of men's shoes (y-axis) and the regression line on the same plot. 

```{r}




```



21) (2points) Construct a scatter plot for height of women (x-axis) and size of women's shoes (y-axis)



```{r}


```

22) (2points) Find a linear correlation coefficient between height of women and size of women's shoes .


```{r}



```
  
  
**What is a linear correlation coefficient? What is the strength of relationship? **


23) (2points) Find regression line for height of women (x-variable) and size of women's shoes (y-variable)


```{r}


```

**What is a regression line?**
 
24) (2points) Construct a scatter plot for height of women (x-axis) and size of women's shoes (y-axis) and the regression line on the same plot. 

```{r}



```





