

---
title: "Quiz 6 (R-Studio)"
author: "Joey Simone"
output:
  word_document: default
---


Given data set with the ages of the best actors and best actresses. 

1. Load Data from excel file into Rstudio. 


```{r}
data=read.csv("income.csv")



```

2. Provide summary of data.

```{r}

summary(data)

```

3. Create bar plot for Marital Status variable. 

```{r}

marital_freq <- table(data$Marital_Status) 
marital_freq

barplot(marital_freq[order(marital_freq, decreasing = T)],
        
        col = rainbow(5),       
        border = "blue",      
         ylim=c(0,50),
        main = "Marital Status",
        ylab = "Number of People", 
        
    
 
       
        
        )




```

 4. (2 point) Create bar plot for Degree variable. 
 
 
```{r}



degree_freq <- table(data$Degree) 
degree_freq

barplot(degree_freq[order(degree_freq, decreasing = T)],
        
        col = rainbow(3),       
        border = "blue",      
         ylim=c(0,50),
        main = "Degree",
        ylab = "Number of People", 
)
        
    


```

5. Create pie chart for Marital Status variable. 


```{r}


pie(degree_freq,
      col = rainbow(5),       
      
      main = "Degree Status")
```
       



6. (2 point) Create pie chart for Degree variable.

```{r}
pie(marital_freq,
      col = rainbow(5),       
      
      main = "Marital Status")




```






7. (2 point) Construct histogram with seven bars for people's ages.

```{r}



```



8. (1 point) Find the mode for people age's.

```{r}




```

**The mode is ** 




9. Construct histogram for people's income when people have high school degree. (number of bars can be chosen by default in R-studio) .


```{r}


hist(data$Income[data$Degree=="High School"], 
     
      main="Income-High School Degree ",
     ylab="Frequency",
     xlab="Income",
    ylim=c(0,20),
     col="Blue", 
     border="red")

```



10. (2 point) Construct histogram for people's income when people have Bachelor Degree (number of bars can be chosen by default in R-studio) .

```{r}



```








11. (2 point) Construct boxplot for people's income when people have high school degree. 

```{r}






```

**Does boxplot have outliers? If so, how many outliers?**







12.  Construct three Box Plots for people's income (one with people who have High School Degree, the other who have Bachelor degree and last one who have Graduate degree) on the same plot. 

```{r}

boxplot(data$Income[data$Degree=="High School"], 
     data$Income[data$Degree=="Bachelor"],
     data$Income[data$Degree=="Graduate"], 
      names=c("High School", "Bachelor","Graduate" ),
   
     xlab="Income",
          col="Blue", 
     border="red",
 horizontal = T)


```





13 (2 point)  Construct two Box Plots for people's income (one for Female and the other for Male) on the same plot. 

```{r}




```




14. (1 point) Compare these two box plots and describe the differences between these two box plots. Does anyone boxplot has outliers? If so, how many outliers? 


15. (2 point) Construct three Box Plots for people's number years in school (one with people who have High School Degree, the other who have Bachelor degree and last one who have Graduate degree) on the same plot. 

```{r}



```




16. (1 point) Compare these three box plots and describe the differences between these two box plots. Does anyone boxplot has outliers? If so, how many outliers? 



17. Find the mean of people's income when people have high school degree.

```{r}

mean(data$Income[data$Degree=="High School"])

```
18. (1 point) Find the mean of people's income for Male.


```{r}


```

19. (1 point) Find the median of people's income when people have Graduate Degree.



```{r}


```



20. (1 point) Find three standard deviations for people's income (one with people who have High School Degree, the other who have Bachelor degree and last one who have Graduate degree) 
```{r}

       

```

**Compare these standard deviations: **



